---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coLCA

<!-- badges: start -->
<!-- badges: end -->

The goal of coLCA is to create some additional functionality for the poLCA package. It provides convenience functions to improve workflow and some additional statistics (cAIC, aBIC and the LMR LRT). 

## Installation

You can install the development version of coLCA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("naokoski/coLCA")
```

## Usage

coLCA provides convenience functions for estimating all the required latent class models from a single function call, which also calculates additional information criteria (consistent AIC and sample-adjusted BIC), not provided in poLCA. A second function extracts all the model selectcion statistics and outputs them as a dataframe for easy comparison; the function also compares each model of k classes to the model of k+1 classes using the Lo-Mendell-Rubin Likelihood Ratio Test that is not available in poLCA.  

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}

#library(coLCA)

##' It is common, when performing Latent Class Analysis, 
##' that the researcher will estimate a number of models 
##' each with an additional class, which will then be compared
##' using statistics and the researcher's own judgment,
##' in order to choose the model which performs best and 
##' at the same time fits well with current knowledge.
##' 
##' When using the poLCA package, each model needs to be
##' run individually and each of the results saved.
##' 
##' This package provides a convenience function so that 
##' the researcher can provide the maximum number of classes
##' they wish to estimate and the function will return
##' a list containing all the model outputs between 
##' one and the maximum number of classes set by the researcher.
##' 
##' Estimate latent class models with 1,2,3 and 4 classes
##' Each model to iterate up to 5,000 times and repeated 10 times.
##' 
##' data(election)
##' 
##' Define the model (the example is of a latent class model with no covariates)
##' f <- cbind(MORALG,CARESG,KNOWG,LEADG,DISHONG,INTELG,MORALB,CARESB,KNOWB,LEADB,DISHONB,INTELB) ~ 1
##' 
##' The argument k is the only argument not included in the poLCA() function. All other arguments are the same.
##' lc_models <- estimateModels(formula = f, data = election, k = 4, maxiter = 5000, nrep = 10)
```

